---
title: "Mental Health Survey"
author: "Sowmya Shree Nagaraju"
date: "4/17/2020"
output:
  word_document: default
  html_document: default
  pdf_document: default
---


```{r pressure, echo=FALSE}
library(dplyr)
library(ggplot2)
library(readxl)
library(tidyverse)
library(ggforce)
library(ggrepel)
library(gridExtra)
library(class)
library(gmodels)
library(caTools)
library(neuralnet)
library(stats)
library(base)


```


```{r}
df<-read.csv("Data.csv")
df<-df[,-1]
```

```{r}
#----------------------------------------------------------------------------------#
# Data Cleaning
#----------------------------------------------------------------------------------#

# Column: Are you Self Employed? 
df[which(df[,2] == "0"),2]<-"No"
df[which(df[,2] == "1"),2]<-"Yes"

# Column: Is your employer tech company?
df[which(df[,4] == "0"),4]<-"No"
df[which(df[,4] == "1"),4]<-"Yes"

# Column:Is your primary role in the company related to tech/IT?
df[which(df[,5] == "0"),5]<-"No"
df[which(df[,5] == "1"),5]<-"Yes"


# Column: How many Employees does your company have?
levels(df$EmployeeCount)
levels(df$EmployeeCount)[1]<-"1-5"
levels(df$EmployeeCount)[3]<-"100-500"
levels(df$EmployeeCount)[4]<-"26-100"
levels(df$EmployeeCount)[5]<-"6-25"
levels(df$EmployeeCount)[7]<-"More than 1000"


# Column: Self employed?
df$SelfEmployed<-factor(df$SelfEmployed)

# Column: Is your employer Tech company?
df$TechCompany<-factor(df$TechCompany)

# Column: Is your primary role in your company is tech related?
df$PrimeRoleInTech<-factor(df$PrimeRoleInTech)

# Column: Requesting for leave 

levels(df$RequestingMedicalLeave)[7]<-"Difficult"

# Column: Discussing with supervisor

levels(df$ComfortDiscussingMentalHealthWithSupervisor)[1]<-"NA"

# Column: Local or online resource

levels(df$LocalOrOnlineResources)[1]<-"NA"


# Column: Previous employers

df[which(df[,22] == "0"),22]<-"No"
df[which(df[,22] == "1"),22]<-"Yes"

# Column: Awareness of Mental health Benefits
levels(df$AwarenessOfMHealthBenefitsPE)[1]<-"No"
levels(df$AwarenessOfMHealthBenefitsPE)[2]<-"Yes"

# Column: Did your previous employer formally discuss Mental health benifits
levels(df$DiscussionPE)[2]<-"No"
levels(df$DiscussionPE)[3]<-"Yes"

# Column: Negative Impact from client
df[which(df[,17] == "No, because it would impact me negatively"),17]<-"Yes"

# Column: Previous Employer
df$PreviousEmployers<-factor(df$PreviousEmployers)


# Column: Previous Health Benefits
levels(df$PreviousMentalHealthBenefits)[2]<-"No"
levels(df$PreviousMentalHealthBenefits)[3]<-"Yes"


# Column: Anonimity Protected by Previous employer
levels(df$AnonymityProtectedPE)[2]<-"No"
levels(df$AnonymityProtectedPE)[3]<-"Yes"

# Column: Comfort discussing with previous employers supervisor
levels(df$ComfortDiscussingMentalHealthWithSupervisorPE)[2]<-"No"
levels(df$ComfortDiscussingMentalHealthWithSupervisorPE)[3]<-"Yes"

# Column: Do you have Medical coverage(Private)

levels(df$MedicalCoverage)[1]<-"No"
levels(df$MedicalCoverage)[2]<-"Yes"


# Column: If you have revealed a mental health issue to a client or 
#         business contact, do you believe this has impacted you negatively?

levels(df$NegativeImpactFromClients)[5]<-"Yes"



# Column: Did your previous employers provide resources to learn more 
#         about mental health issues and how to seek help?

levels(df$ResourcesPE)[1]<-"No"
levels(df$ResourcesPE)[2]<-"Yes"



# Column: Gender
df$Gender<-tolower(df$Gender)
df[which(df$Gender %in% c("male","male","man","cis male","male.","male 9:1 female, roughly","male (cis)","nb masculine",
                                  "sex is male","malr","mtf","dude",
                                  "mail","m|","male/genderqueer","male (trans, ftm)","cisdude","cis man","cis-male",
                                  "male/androgynous","cis hetero male","m",
                                  "male, cis","cis male","male-ish","ostensibly male",
                                  "malel","cisgender male","identify as male",
                                  "masculine","cishet male","masculino","make")),39]<-"Male"


df[which(df$Gender %in% c("female","female ","cis female "," female","femalw","femail",
                                "female (cisgender)","female (cis)","cis-female","cis female","cis woman",
                                "femile")),39]<-"Female"

df[!(df$Gender=="Male"|df$Gender=="Female"),39]<-"Trans"
df$Gender<-factor(df$Gender)

# Age
# Max age is 323, min age is 3.
# There are only 5 people that have weird ages (3yo, 15yo, or 99yo or 323 yo.) 
# These people will take the average age of the dataset (the correct calculated one, w/out outliers)

df_age<-df[which(df$Age >= 18 & df$Age<= 75),38]
age<-mean(df_age)
age<-round(age,digits = 0)
df[(which(df$Age < 18 | df$Age > 75 | is.na(df$Age))),38]<-age



# Column: Negative impact from client

levels(df$NegativeImpactFromClients)[4]<-"Yes"
levels(df$NegativeImpactFromClients)[6]<-"No"
levels(df$NegativeImpactFromClients)[7]<-"No"


# Column: Negative response from colleagues

levels(df$NegativeResponseFromCollegues)[3]<-"Yes"
levels(df$NegativeResponseFromCollegues)[7]<-"No"
levels(df$NegativeResponseFromCollegues)[5]<-"No"

# Column: Comfort discussing with coworker

levels(df$ComfortDiscussingMentalHealthWithCoworkers)[3]<-"Yes"
levels(df$ComfortDiscussingMentalHealthWithCoworkers)[5]<-"No"
levels(df$ComfortDiscussingMentalHealthWithCoworkers)[6]<-"Yes"

# Column: awareness of Mental Health Benefits
df$AwarenessOfMHealthBenefitsPE<-factor(df$AwarenessOfMHealthBenefitsPE)
levels(df$AwarenessOfMHealthBenefitsPE)[1]<-"No"
levels(df$AwarenessOfMHealthBenefitsPE)[2]<-"Yes"


# Column: Resource provided by Previous employer
df$ResourcesPE<-factor(df$ResourcesPE)
levels(df$ResourcesPE)[1]<-"No"
levels(df$ResourcesPE)[2]<-"Yes"

# Column: Comfort discussing with previous coworker
df$ComfortDiscussingMentalHealthWithCoworkersPE<-
  factor(df$ComfortDiscussingMentalHealthWithCoworkersPE)
levels(df$ComfortDiscussingMentalHealthWithCoworkersPE)[1]<-"No"
levels(df$ComfortDiscussingMentalHealthWithCoworkersPE)[2]<-"Yes"

# Column: Negative impact on Career
df$NegativeImpactOfIssuesOnCareer<-factor(df$NegativeImpactOfIssuesOnCareer)
levels(df$NegativeImpactOfIssuesOnCareer)[1]<-"No"
levels(df$NegativeImpactOfIssuesOnCareer)[2]<-"Yes"


# Column: Observed or experienced bad response from previous employer
levels(df$ObservedOrExperiencedBadResponseCEPE)[2]<-"No"
levels(df$ObservedOrExperiencedBadResponseCEPE)[3]<-"Yes"
levels(df$ObservedOrExperiencedBadResponseCEPE)[1]<-"No"
levels(df$ObservedOrExperiencedBadResponseCEPE)[4]<-"No"
levels(df$ObservedOrExperiencedBadResponseCEPE)
summary(df$ObservedOrExperiencedBadResponseCEPE)

# Column: family history
df$FamilyHistory<-factor(df$FamilyHistory)
levels(df$FamilyHistory)[1]<-"No"
levels(df$FamilyHistory)[2]<-"Yes"

# Column: Diagnosis
df$Diagnosis<-factor(df$Diagnosis)
levels(df$Diagnosis)[1]<-"No"
levels(df$Diagnosis)[2]<-"Yes"

levels(df$MentalHealthDisorder)
levels(df$MentalHealthDisorder)[1] <- "No"
summary(df$MentalHealthDisorder)

levels(df$MentalHealthBenefits)

rm(age,df_age)


#----------------------------------
# After cleaning the data

head(df)
summary(df)

dfCopy <- df

write.csv(df,'DataUpdated.csv')

```


```{r}
df <- read.csv("DataUpdated.csv")
dfCopy <- df
```


```{r}
# Visualization
df1<-df%>%group_by(df$SelfEmployed,df$TechCompany)%>%
          dplyr::summarise(count = n())
colnames(df1)<-c("Self_employed","TechCompany","count")
ggplot(df1, aes(x=Self_employed, y=count, fill=TechCompany)) + 
  geom_bar(position = "stack",stat = "identity",width = 0.5) +
  labs(x="Self Employed", y="Number of Sefl employed people",title ="Overview of Self employed and Tech Company data") +
  theme_light()+theme(plot.title = element_text(family="Times New Roman", 
                                                face="bold.italic",color="black",size=14),
                      text = element_text(family="Times New Roman", 
                                          face="bold.italic",color="black",size=10),
                      legend.key.size = unit(0.3, "cm"),
                      legend.position = "top") +
  geom_text(aes(label = df1$count), vjust = 0.4, position = position_stack(vjust = 0.5))


ggsave("TechCompany.png", device="png", dpi = 1000)
```


```{r}
# Number of Respondents by Country and Tech flag
df1<-df%>%group_by(WorkCountry,TechCompany)%>%
          dplyr::summarise(count=n())%>%arrange(desc(count))
df1<-df1[1:8,]
df1$WorkCountry<-as.character(df1$WorkCountry)
df1[which(df1$WorkCountry =="United States of America"),1]<-"USA"
df1[which(df1$WorkCountry =="United Kingdom"),1]<-"UK"

ggplot(df1, aes(x=reorder(WorkCountry,-count), y=count, fill=TechCompany)) + 
  geom_bar(position = "dodge",stat = "identity",width = 0.5) +
  labs(x="Country", y="Count",title ="Number of Respondents by Country and Tech flag ") +
  theme_light()+theme(plot.title = element_text(family="Times New Roman", 
                                                face="bold.italic",color="black",size=14),
                      text = element_text(family="Times New Roman", 
                                          face="bold.italic",color="black",size=10),
                      legend.key.size = unit(0.3, "cm"),
                      legend.position = "top")
ggsave("NoResbyCountry.png", device="png", dpi = 1000)
```

```{r}
# Number of Respondents by Company size and tech flag

df1<-df%>%group_by(EmployeeCount,TechCompany)%>%
  dplyr::summarise(count=n())%>%arrange(desc(count))


ggplot(df1, aes(x=EmployeeCount, y=count, fill=TechCompany)) + 
  geom_bar(position = "dodge",stat = "identity",width = 0.5) +
  labs(x="Company size", y="Count",title ="Number of Respondents by Company size and tech flag") +
  theme_light()+theme(plot.title = element_text(family="Times New Roman", 
                                                face="bold.italic",color="black",size=14),
                      text = element_text(family="Times New Roman", 
                                          face="bold.italic",color="black",size=10),
                      legend.key.size = unit(0.3, "cm"),
                      legend.position = "top")
ggsave("NoResbyCompanysize.png", device="png", dpi = 1000)
```


```{r}
# Gender (only Tech)

df1<-df%>%group_by(WorkCountry,Gender)%>%
  dplyr::summarise(count=n())%>%arrange(desc(count))

df1$WorkCountry<-as.character(df1$WorkCountry)
df1[which(df1$WorkCountry =="United States of America"),1]<-"USA"
df1[which(df1$WorkCountry =="United Kingdom"),1]<-"UK"
df1<-df1[which(df1$WorkCountry=="USA"|df1$WorkCountry=="UK"|
                df1$WorkCountry=="Canada"|df1$WorkCountry=="Germany"|
                 df1$WorkCountry=="Netherlands"|df1$WorkCountry=="Australia"),]



ggplot(df1, aes(x=reorder(WorkCountry,-count), y=count, fill=Gender)) + 
  geom_bar(position = "dodge",stat = "identity",width = 0.5) +
  labs(x="Country", y="Count",title ="Gender by Country") +
  theme_light()+theme(plot.title = element_text(family="Times New Roman", 
                                                face="bold.italic",color="black",size=14),
                      text = element_text(family="Times New Roman", 
                                          face="bold.italic",color="black",size=10),
                      legend.key.size = unit(0.3, "cm"),
                      legend.position = "top")
ggsave("NoResbyCompanysize.png", device="png", dpi = 1000)

```


```{r}
# Overall gender prop pie chart

df1<-df%>%group_by(Gender)%>%
          dplyr::summarise(count=n())

df2<-df1%>%mutate(Group = factor(Gender, levels = c("Male", "Female", "Trans")),
           cumulative = cumsum(count),
           midpoint = cumulative - count / 2,
           label = paste0(Gender, " ", round(count / sum(count) * 100, 1), "%"),1)

ggplot(df2, aes(x = 1, weight = count, fill = Gender)) +
  geom_bar(width = 1, position = "stack") +
  coord_polar(theta = "y") +
  geom_text(aes(y = midpoint, label = label))+
  theme_void()

ggsave("Genderratio.png", device="png", dpi = 1000)

```

```{r}
# Mental health disorder current

df1<-df%>%group_by(WorkCountry,MentalHealthDisorder)%>%
          dplyr::summarise(count=n())%>%arrange(desc(count))%>%drop_na()

df1$WorkCountry<-as.character(df1$WorkCountry)
df1[which(df1$WorkCountry =="United States of America"),1]<-"USA"
df1[which(df1$WorkCountry =="United Kingdom"),1]<-"UK"
df1<-df1[which(df1$WorkCountry=="USA"|df1$WorkCountry=="UK"|
                 df1$WorkCountry=="Canada"|df1$WorkCountry=="Germany"|
                 df1$WorkCountry=="Netherlands"|df1$WorkCountry=="Australia"),]

par(mfrow=c(1,2))

# Bar graph
ggplot(df1, aes(x=reorder(WorkCountry,-count), y=count, fill=MentalHealthDisorder)) + 
  geom_bar(position = "dodge",stat = "identity",width = 0.5) +
  labs(x="Country", y="Count",title ="Mental Health Disorder by Country") +
  theme_light()+theme(plot.title = element_text(family="Times New Roman", 
                                                face="bold.italic",color="black",size=14),
                      text = element_text(family="Times New Roman", 
                                          face="bold.italic",color="black",size=10),
                      legend.key.size = unit(0.3, "cm"),
                      legend.position = "top")
ggsave("MentalHealthDisorder.png", device="png", dpi = 1000)
```


```{r}
# Pie chart to show the mental health history disorder ratio

df1<-df%>%group_by(PersonalHistory)%>%
  summarise(count=n())
df2<-df1%>%mutate(Group = factor(PersonalHistory, levels = c("Yes", "No", "Don't Know")),
                  cumulative = cumsum(count),
                  midpoint = cumulative - count / 2,
                  label = paste0(PersonalHistory, " ", round(count / sum(count) * 100), "%"),1)
df2<-df2%>%drop_na()
ggplot(df2, aes(x = 1, weight = count, fill = PersonalHistory)) +
  geom_bar(width = 1, position = "stack") +
  coord_polar(theta = "y") +
  geom_text(aes(y = midpoint, label = label),position = position_stack(vjust = 0.5))+
  theme_void()+theme(legend.position = "bottom",
                     legend.key.size = unit(0.3, "cm"),
                     text = element_text(family="Times New Roman", 
                                         face="bold.italic",color="black",size=10))


ggsave("Mentalhealthhistory.png", device="png", dpi = 1000)
```

```{r}
# Does your employer provide mental health benefits as part of healthcare coverage?


df1<-df%>%group_by(EmployeeCount,MentalHealthBenefits)%>%
  summarise(count=n())

ggplot(df1, aes(x=reorder(EmployeeCount,-count), y=count, fill=MentalHealthBenefits)) + 
  geom_bar(position = "dodge",stat = "identity",width = 0.5) +
  labs(x="Country", y="Count",title ="Ratio of Employers who provide Mental Health Benefits") +
  theme_light()+theme(plot.title = element_text(family="Times New Roman", 
                                                face="bold.italic",color="black",size=14),
                      text = element_text(family="Times New Roman", 
                                          face="bold.italic",color="black",size=10),
                      legend.key.size = unit(0.3, "cm"),
                      legend.position = "top")
ggsave("Mentalhealthbenefits.png", device="png", dpi = 1000)
```


```{r}
# Does your employer offer resources to learn more about mental health concerns and options for seeking help?

df1<-df%>%group_by(ResourcesAvailable)%>%
  summarise(count=n())
df2<-df1%>%mutate(Group = factor(ResourcesAvailable, levels = c("Yes", "No", "Don't Know")),
                  cumulative = cumsum(count),
                  midpoint = cumulative - count / 2,
                  label = paste0(ResourcesAvailable, " ", round(count / 3000 * 100), "%"),1)
ggplot(df2, aes(x = 1, weight = count, fill = ResourcesAvailable)) +
  geom_bar(width = 1, position = "stack") +
  coord_polar(theta = "y") +
  geom_text(aes(y = midpoint, label = label))+
  theme_void()+ labs(title = "Mental Health Resources Provided")+
  theme(legend.position = "right",
        legend.key.size = unit(0.5, "cm"),
        text = element_text(family="Times New Roman", 
                            face="bold.italic",color="black",size=12))

```

```{r}
#--------------------------------------------------------------------------------------------#
#           Data Preparation
#--------------------------------------------------------------------------------------------#

df<-filter(df,df$TechCompany == "Yes")
levels(df$MentalHealthDisorder)
levels(df$MentalHealthDisorder)[1] <- 0
levels(df$MentalHealthDisorder)[2] <- 1
levels(df$FamilyHistory)
levels(df$FamilyHistory)[1] <- 0
levels(df$FamilyHistory)[2] <- 1

MentalHealth<-df[,c("Age","Gender","FamilyHistory","MentalHealthBenefits","OptionsAvailable",
                    "AnonymityProtected","RequestingMedicalLeave","InterferenceWithWorkEnv",
                    "PersonalHistory","MentalHealthDisorder")]
# Finding the missing values
sapply(MentalHealth, function(x) sum(is.na(x)))
# Deleting the missing values
MentalHealth <- MentalHealth[!is.na(MentalHealth$InterferenceWithWorkEnv),]


summary(MentalHealth)
MentalHealth1<-MentalHealth[,-3]
must_convert<-sapply(MentalHealth1[,-9],is.factor)  # logical vector telling if a variable needs to be displayed as numeric
M2<-sapply(MentalHealth1[,must_convert],unclass)    # data.frame of all categorical variables now displayed as numeric
out<-cbind(MentalHealth1[,!must_convert],M2)        # complete data.frame with all variables put together
str(out)
out <- data.frame(out)
out$FamilyHistory<-MentalHealth$FamilyHistory

```


```{r}
# Corelation Matrix
must_convert<-sapply(MentalHealth,is.factor)       # logical vector telling if a variable needs to be displayed as numeric
M2<-sapply(MentalHealth[,must_convert],unclass)    # data.frame of all categorical variables now displayed as numeric
out<-cbind(MentalHealth[,!must_convert],M2)        # complete data.frame with all variables put together

str(out)
out <- data.frame(out)
colnames(out)[1] <-"Age"
cormat <- round(cor(out),2)
head(cormat)
library(reshape2)

# Get lower triangle of the correlation matrix
get_lower_tri<-function(cormat){
  cormat[upper.tri(cormat)] <- NA
  return(cormat)
}
# Get upper triangle of the correlation matrix
get_upper_tri <- function(cormat){
  cormat[lower.tri(cormat)]<- NA
  return(cormat)
}

upper_tri <- get_upper_tri(cormat)
upper_tri

melted_cormat <- melt(upper_tri, na.rm = TRUE)
# Heatmap
ggplot(melted_cormat, aes(Var2, Var1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "plum2", high = "darkmagenta", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Correlation") +
  theme_minimal()+ # minimal theme
  theme(axis.text.x = element_text(angle = 90, vjust = 1, 
                                   size = 9, hjust = 1))+
  coord_fixed()


ggsave("correlation.png", device="png", dpi = 1000)

```


```{r}
#--------------------------------------------------------------------------------------------#
#     Data Modeling
#--------------------------------------------------------------------------------------------#
# KNN Method

library(fastDummies)
MentalHealth1 <- fastDummies::dummy_cols(out, select_columns = c("Gender","MentalHealthBenefits","OptionsAvailable",
                        "AnonymityProtected","RequestingMedicalLeave","InterferenceWithWorkEnv","PersonalHistory"))

MentalHealth<-MentalHealth1[,-c(3:9)]
#Dividing dataset into train(60%) and test(40%)

library(caTools)
set.seed(125)
sample <- sample.split(MentalHealth, SplitRatio = 0.60)
train <- subset(MentalHealth, sample == TRUE)
test <- subset(MentalHealth, sample == FALSE)
MentalHealth_train<-train[,-2]
MentalHealth_test<-test[,-2]
train.def<-train$MentalHealthDisorder
test.def<-test$MentalHealthDisorder
#For k=1
knn_pred.result1 <- knn(MentalHealth_train, MentalHealth_test, train.def, k=1 )
table(knn_pred.result1, test.def)
misClassificError <- mean(knn_pred.result1 != test.def)
print(paste('Accuracy', 1-misClassificError))

#For k=2
knn_pred.result2 <- knn(MentalHealth_train, MentalHealth_test, train.def, k=2 )
table(knn_pred.result2, test.def)
misClassificError <- mean(knn_pred.result2 != test.def)
print(paste('Accuracy', 1-misClassificError))

#For k=3
knn_pred.result3 <- knn(MentalHealth_train, MentalHealth_test, train.def, k=3 )
table(knn_pred.result3, test.def)
misClassificError <- mean(knn_pred.result3 != test.def)
print(paste('Accuracy', 1-misClassificError))

#For k=4
knn_pred.result4 <- knn(MentalHealth_train, MentalHealth_test, train.def, k=4 )
table(knn_pred.result4, test.def)
misClassificError <- mean(knn_pred.result4 != test.def)
print(paste('Accuracy', 1-misClassificError))

#For k=5
knn_pred.result5 <- knn(MentalHealth_train, MentalHealth_test, train.def, k=5 )
table(knn_pred.result5, test.def)
misClassificError <- mean(knn_pred.result5 != test.def)
print(paste('Accuracy', 1-misClassificError))

#For k=6
knn_pred.result6 <- knn(MentalHealth_train, MentalHealth_test, train.def, k=6 )
table(knn_pred.result6, test.def)
misClassificError <- mean(knn_pred.result6 != test.def)
print(paste('Accuracy', 1-misClassificError))

#For k=7
knn_pred.result7 <- knn(MentalHealth_train, MentalHealth_test, train.def, k=7 )
table(knn_pred.result7, test.def)
misClassificError <- mean(knn_pred.result7 != test.def)
print(paste('Accuracy', 1-misClassificError))

#For k=8
knn_pred.result8 <- knn(MentalHealth_train, MentalHealth_test, train.def, k=8 )
table(knn_pred.result8, test.def)
misClassificError <- mean(knn_pred.result8 != test.def)
print(paste('Accuracy', 1-misClassificError))

#For k=9
knn_pred.result9 <- knn(MentalHealth_train, MentalHealth_test, train.def, k=9 )
table(knn_pred.result9, test.def)
misClassificError <- mean(knn_pred.result9 != test.def)
print(paste('Accuracy', 1-misClassificError))

#For k=10
knn_pred.result10 <- knn(MentalHealth_train, MentalHealth_test, train.def, k=10 )
table(knn_pred.result10, test.def)
misClassificError <- mean(knn_pred.result10 != test.def)
print(paste('Accuracy', 1-misClassificError))


# We get the highest accuracy at k= 3 with accuracy of 87.62%

```


```{r}
#---------------------------------------------------------------------------------------
# Decision Tree CANCELLED

library(rpart)
library(rpart.plot)

CT_model1 <- rpart(MentalHealthDisorder ~ ., data = train, method = 'class')
printcp(CT_model1)
rpart.plot(CT_model1, type = 1, extra = 1, split.font = 1, varlen = -10)
summary(CT_model1)

CT_pred.result1 <-predict(CT_model1, test, type = 'class')

table(CT_pred.result1, test.def)
misClassificError <- mean(CT_pred.result1 != test.def)
print(paste('Accuracy', 1-misClassificError))

# Considering all predictors, we got model accuracy 80.49%
# Let's consider predictors with importance more than 10.

CT_model2 <- rpart(MentalHealthDisorder ~ PersonalHistory_2 + PersonalHistory_3 + InterferenceWithWorkEnv_1,
                   data = train, method = 'class')
printcp(CT_model2)
rpart.plot(CT_model2, type = 1, extra = 1, split.font = 1, varlen = -10)
summary(CT_model2)

CT_pred.result2 <-predict(CT_model2, test, type = 'class')

table(CT_pred.result2, test.def)
misClassificError <- mean(CT_pred.result2 != test.def)
print(paste('Accuracy', 1-misClassificError))

# Accuracy didnt improve after removing non important variables

#---------------------------------------------------------------------------------------
```


```{r}
#Multiple Linear Regression Model CANCELLED
str(out)
library(car)
RegModel <- lm(V1 ~ MentalHealthDisorder + AnonymityProtected + PersonalHistory ,data = out)
summary(RegModel)
par(mfrow=c(2,2))
plot(RegModel)

#The Normal QQ plot shows that there is a linear relationship between a person having 
```

```{r}
#Neural Net
library(caret)
library(neuralnet)
normalize <- function(x) {
   return ((x - min(x)) / (max(x) - min(x)))
}
train2<- train
train2<-lapply(train2, normalize)
train2<-data.frame(train2)

test2<- test
test2<-lapply(test2, normalize)
test2<-data.frame(test2)

nn1 <- neuralnet(MentalHealthDisorder ~  .-Gender,train2, hidden = 3)
training.prediction1 <-neuralnet::compute(nn1, train2)
trainProb1<- training.prediction1$net.result
NNresults <- data.frame(actual = train2$MentalHealthDisorder, prediction = trainProb1)

roundedresults<-sapply(NNresults,round,digits=0)
roundedresultsdf<-data.frame(roundedresults)
attach(roundedresultsdf)
conmat <- confusionMatrix(table(actual,prediction)[,-3])
conmat

#We get an accuracy of 85.22% on the training dataset

test.prediction1 <- neuralnet::compute(nn1, test2)
testProb1<- test.prediction1$net.result
NN.Testresults <- data.frame(actual = test2$MentalHealthDisorder, prediction = testProb1)

roundedresults2<-sapply(NN.Testresults,round,digits=0)
roundedresultsdf2<-data.frame(roundedresults2)
attach(roundedresultsdf2)
conmat2 <- confusionMatrix(table(actual,prediction)[,-3])
conmat2 <- confusionMatrix(table(actual,prediction))
conmat2
table(factor(prediction, levels=min(test):max(test)), 
      factor(actual, levels=min(test):max(test)))

plot(nn1)
plot(nn2)

#We get an accuracy of 86.57% on the Test set
```


```{r}
dfCopy<-filter(dfCopy,dfCopy$TechCompany == "Yes")
df.MentalHealth <- dfCopy[,c("SelfEmployed","EmployeeCount","OptionsAvailable","PreviousEmployers","PreviousMentalHealthBenefits","DiscussionPE","NegativeImpactOfIssuesOnCareer","FamilyHistory","PersonalHistory","MentalHealthDisorder","InterferenceWithWorkEnv","Age","Gender")]

str(df.MentalHealth)
levels(df.MentalHealth$OptionsAvailable)
levels(df.MentalHealth$OptionsAvailable)[2]<-"I don't know"
levels(df.MentalHealth$PreviousMentalHealthBenefits)[1] <- "I don't know"
levels(df.MentalHealth$DiscussionPE)[1] <- "I don't know"


sample <- sample.split(df.MentalHealth, SplitRatio = 0.60)
train <- subset(df.MentalHealth, sample == TRUE)
test <- subset(df.MentalHealth, sample == FALSE)

train.def<-train$MentalHealthDisorder
test.def<-test$MentalHealthDisorder
```

```{r}
#DecisionTree

library(rpart)
library(rpart.plot)

DT_model1 <- rpart(MentalHealthDisorder ~ ., data = train, method = 'class' , cp= 0.005, maxdepth = 4)
printcp(DT_model1)
rpart.plot(DT_model1, type = 1, extra = 1, split.font = 1, varlen = -10)
summary(DT_model1)

DT_predTrain <-predict(DT_model1, train, type = 'class')
DT_predTest <- predict(DT_model1, test, type = 'class')

table(DT_predTrain, train.def)
table(DT_predTest, test.def)

misClassificErrorTrain <- mean(DT_predTrain != train.def)
misClassificErrorTest <- mean(DT_predTest != test.def)

print(paste('Accuracy of Training model = ', 1-misClassificErrorTrain))
print(paste('Accuracy of Testing model = ', 1-misClassificErrorTest))

```

```{r}
#RandomForest Incomplete
library(randomForest)
RF_model <- randomForest(MentalHealthDisorder ~ ., data = train, importance = TRUE , na.action=na.roughfix)
getTree(RF_model)


print(RF_model)
RF_Predict <- predict(RF_model, train)

```

```{r}
#Naive Bayes
x <- train[,-10]
y <- train$MentalHealthDisorder

library(e1071)
library(caret)

NBModel <- naiveBayes(x , y , trControl=trainControl(method='cv',number=10))
NBModel

NBPredictTraining <- predict(NBModel, newdata = train)
NBtrainTable=table(train$MentalHealthDisorder, NBPredictTraining)
trainAcc=(NBtrainTable[1,1]+NBtrainTable[2,2])/sum(NBtrainTable)

NBPredictTest <- predict(NBModel, newdata = test)
NBtestTable=table(test$MentalHealthDisorder, NBPredictTest)
testAcc=(NBtestTable[1,1]+NBtestTable[2,2])/sum(NBtestTable)
print(paste('Training Accuracy =', trainAcc))
print(paste('Testing Accuracy =', testAcc))

```

```{r}
#Logistic Regression

logisticModel <- glm( MentalHealthDisorder~ ., data = train ,family='binomial')
summary(logisticModel)
#Predict Output
library(ROCR)
LogisticPredictTrain= predict(logisticModel,train[,-10])
predTrain <- ROCR::prediction(LogisticPredictTrain, train$MentalHealthDisorder) 
prfTrain <- performance(predTrain, measure = "tpr", x.measure = "fpr")
plot(prfTrain , main = "Training ROC curve")

aucTrain <- performance(predTrain, measure = "auc")
aucTrain <- aucTrain@y.values[[1]]
aucTrain

#AUC gives the performance = 82.46% in the train set

LogisticPredict= predict(logisticModel,test[,-10])
pred <- ROCR::prediction(LogisticPredict, test$MentalHealthDisorder) 
prf <- performance(pred, measure = "tpr", x.measure = "fpr")
plot(prf , main = "Test ROC curve")

auc <- performance(pred, measure = "auc")
auc <- auc@y.values[[1]]
auc

#AUC gives the performance = 75.52% in the test set
```





```{r}
#SVM 

library(e1071)
SVMmodel<-svm(MentalHealthDisorder~. , data = train2 , type = 'C-classification', kernel = 'linear', cost=10, na.action=na.omit)
summary(SVMmodel)
SVMpredict = predict(SVMmodel,train2[,-3])

#Confusion Matrix SVM
SVMTable <- table(train2[,3],SVMpredict)
SVMTable

SVMaccuracy<-(SVMTable[1,1]+SVMTable[2,2])/(SVMTable[1,1]+SVMTable[1,2]+SVMTable[2,1]+SVMTable[2,2])
print(SVMaccuracy)
```


plot(SVMmodel,train2, MentalHealthDisorder~Gender)
 


# PLOT ROC-AUC Curve for SVM
plot(pROC::roc(SVMpredict>.5, train[,10]),main="ROC Curve for SVM",plot=TRUE,print.auc=TRUE )


```

```{r}
#LDA
library(MASS)

ldaModel <- lda(MentalHealthDisorder ~., data=train2)
ldapredict <- predict(ldaModel,newdata = train2)
head(ldapredict$class)
head(ldapredict$posterior)
head(ldapredict$x,3)

prop.lda = ldaModel$svd^2/sum(ldaModel$svd^2)
prop.lda
dataset = data.frame(train2[,3], lda = ldapredict$x)

p1 <- ggplot(dataset) + geom_point(aes(lda.LD1, lda.LD2), size = 2.5) + 
  labs(x = paste("LD1 (", percent(prop.lda[1]), ")", sep=""),
       y = paste("LD2 (", percent(prop.lda[2]), ")", sep=""))

```

```{r}
prop.lda = ldaModel$svd^2/sum(ldaModel$svd^2)
prop.lda
dataset = data.frame(train2[,3], lda = ldapredict$x)

p1 <- ggplot(dataset) + geom_point(aes(lda.LD1, lda.LD2), size = 2.5) + 
  labs(x = paste("LD1 (", percent(prop.lda[1]), ")", sep=""),
       y = paste("LD2 (", percent(prop.lda[2]), ")", sep=""))

p1 <- ggplot(dataset) + geom_point(aes(ldapredict$x, ldaModel.LD2, colour = species, shape = species), size = 2.5)+ 
  labs(x = "LD1",
       y = "LD2")

p1

grid.arrange(p1, p2)


ldapredict.posteriors <- as.data.frame(ldapredict$posterior)
ldapred <- ROCR::prediction(ldapredict, train2$MentalHealthDisorder)
roc.perf = performance(ldapred, measure = "tpr", x.measure = "fpr")
auc <- performance(ldapred, measure = "auc")
auc <- auc@y.values



LogisticPredict= predict(logisticModel,test[,-10])
pred <- prediction(LogisticPredict, test$MentalHealthDisorder) 
prf <- performance(pred, measure = "tpr", x.measure = "fpr")
plot(prf , main = "Test ROC curve")

auc <- performance(pred, measure = "auc")
auc <- auc@y.values[[1]]
auc
# Plot
plot(roc.perf)
abline(a=0, b= 1)
text(x = .25, y = .65 ,paste("AUC = ", round(auc.train[[1]],3), sep = ""))
```


